---
title: "ggeor package"
author: "Kim Josh Hyungyum"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
#Introduction
The main purpose of this vignette is to describe and elaborate the package ggeor which contains 2 functions regarding google maps API. Each function takes data from google maps API and returns address and latitude / longitude.

##gaddress function
This function takes one argument which is restricted as character class. The argument should be an address of existing place and the function takes data from google maps API and returns the address' latitude and longitude as a data.frame.(Basically works as geocoding)

##glatlng function
This function takes one argument which is restricted as character class. The argument should be a combination of latitude and longitude separated by "," with exact order. The function takes data from google maps API and returns the address of the given latitude and longitude as a character string.(Basically works as reverse geocoding)

##Example of gaddress function
```{r}
library(ggeor)

gaddress("Linkoping")
```

##Example of gaddress function
```{r}
glatlng("37.56654, 126.978")
```

